---
title: "`r params$title`"
author: "`r params$org`"
date: "`r params$date`"
output: 
  pdf_document:
    latex_engine: xelatex
geometry: "a4paper, margin=2.5cm"
mainfont: Calibri
fontsize: 10pt
params:
  title: "Exploratory Data Analysis for Learning Analytics"
  subtitle: "Cyber Security students' willingness to sharing personal data"
  org: "Newcastle University - CSC8631 Summative Assignment"
  author: "Issy Middleton - C1000051"
  date: "December 2020"
---

```{r setup, include=FALSE}
# Knitr setup
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
```

```{r include=FALSE}
# Load project
library("ProjectTemplate")
load.project()
# Run code in analysis.R script
source("src/analysis.R")
```

## Summary

words

## Enrolment analysis

A dataset of numerous files in a variety of formats, compressed into a single folder, was provided by the Newcastle programme team for analysis. The material belonged to Learning Analytics and related to a series of an online training course, entitled Cyber Security: Safety at Home, Online, in Life. This report summarises the findings and insights relating to the survey students completed upon enrolment. Given that the training subject was online security I was interested to determine students' attitudes before the course began, and their willingness to provide personal data. 

Seven intakes of the course ran over a period of two years, with the first student enrolled on `r format(firststudentreport)`, the last student enrolled on `r format(laststudentreport)` meaning the seven course series ran over a period of over two and a half years.

### Enrolment - key statistics

In total, `r (enrolcount)` unique student enrolment records were assessed from seven survey files. The first survey file had the most enrolment records but the 'enrolled at' dates had the largest variance.

Survey No.|    Date First Student Enrolled   | Date Last Student Enrolled       |Duration (days) | No. of Students
--------|-----------------------------|------------------------------|--------------| ----------
1   |  `r (cyber1firststudentreport)` | `r (cyber1laststudentreport)`|`r format(cyber1durationdaysunique)` | `r (count1unique)`
2   |  `r (cyber2firststudentreport)` | `r (cyber2laststudentreport)`|`r format(cyber2durationdaysunique)` | `r (count2unique)`
3   |  `r (cyber3firststudentreport)` | `r (cyber3laststudentreport)`|`r format(cyber3durationdaysunique)` | `r (count3unique)`
4   |  `r (cyber4firststudentreport)` | `r (cyber4laststudentreport)`|`r format(cyber4durationdaysunique)` | `r (count4unique)`
5   |  `r (cyber5firststudentreport)` | `r (cyber5laststudentreport)`|`r format(cyber5durationdaysunique)` | `r (count5unique)`
6   |  `r (cyber6firststudentreport)` | `r (cyber6laststudentreport)`|`r format(cyber6durationdaysunique)` | `r (count6unique)`
7   |  `r (cyber7firststudentreport)` | `r (cyber7laststudentreport)`|`r format(cyber7durationdaysunique)` | `r (count7unique)`

\newpage

The 'enrolled at' dates within the files would indicate that the courses overlapped in duration and varied in length, with the volumes of students applying for each course gradually reducing. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert survey response plots
Annual_Survey_Response
Survey_Response

```

words

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert survey response plots

Shared_Gender
Shared_Gender_by_Age
Shared_Age_and_Gender_by_Year
Shared_Gender_by_Age_by_Survey
Shared_MF_by_Age_by_Survey
Shared_MF_by_Age

```

words

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert survey response plots

Shared_Gender_by_Emp_by_Survey

```

Words about employment graphs to follow

```{r echo=FALSE, message=FALSE, warning=FALSE}
Employment_Status_Total
Employment_Area_Total
Employment_Area_by_Year
Employment_Status_by_Year
```


\newpage

## Data and assumptions

### Assumptions

- It is assumed that duplicated learner_id records are exact copies of the same survey response. In total 2071 non-unique learner_id records were removed from the dataset prior to analysis. It was expected that the learner_id being 36 characters in length was expected to be unique and represents a single student. Example, 233b9253-e8e6-4734-8a7f-cb2c7845c85a.


```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert duplicate analysis
Duplicate_Records

```

- It is assumed that each record within the cyber security enrolments files corresponds to a student who provided details that truthfully reflected their gender, employment status and area, age range and highest educational level.

- It is assumed that the data contained within the cyber security enrolments files was provided before the training had commenced.

- It is assumed that each enrolment file relates to a course intake.



### Data summary





**`r params$author`**  
**`r params$org`**  
**`r params$date`**

## Notes

Words
