---
title: "`r params$title`"
author: "`r params$org`"
date: "`r params$date`"
output: 
  pdf_document:
    latex_engine: xelatex
geometry: "a4paper, margin=2.5cm"
mainfont: Calibri
fontsize: 12pt
params:
  title: "Exploratory Data Analysis for Learning Analytics"
  subtitle: "Cyber Security students' willingness to sharing personal data"
  org: "Newcastle University - CSC8631 Summative Assignment"
  author: "Issy Middleton - C1000051"
  date: "December 2020"
---

```{r setup, include=FALSE}
# Knitr setup
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
```

```{r include=FALSE}
# Load project
library("ProjectTemplate")
load.project()
# Run code in analysis.R script
source("src/analysis.R")
```

## Summary

words

## Enrolment analysis

Data was provided by Learning Analytics regarding an online training course, entitled Cyber Security: Safety at Home, Online, in Life. This report summarises finding relating to the survey that student completed at enrollment and specifically reviews the amount of personal data that they are, and are not, willing to provide. The students enrolling on the course over the seven surveys.

The seven courses were run over a period of two years, with intakes starting in September 2016, March 2017, September 2017, November 2017, February 2018, June 2018 and September 2018.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert survey response plots
Survey_Response

Annual_Survey_Response
```

\newpage

## Data and assumptions

Working assumptions:

- Duplicated learner_id records were exact copies of the same survey response. In total 2071 non-unique learner_id records were removed from the dataset prior to analysis. It was expected that the learner_id being 36 characters in length was expected to be unique and represent a single student. Example, 233b9253-e8e6-4734-8a7f-cb2c7845c85a.


```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert duplicate analysis
duplicate_table1

```



### Assumptions

Assumption    | Value
------------- | -------------------------------------
Discount rate | #r paste(100*disc, "% p.a.", sep="")
...           | ...
...           | ...

### Data summary



I look forward to discussing this report with you.

**`r params$author`**  
**`r params$org`**  
**`r params$date`**

## Notes

Eum et tamquam patrioque, has an meliore imperdiet, audiam docendi delicata his ad. Ad solet perfecto vituperata his, ignota appetere mea ad. Id mea mazim consequat, in mei dignissim cotidieque, sed eloquentiam definitiones no. Persius democritum ne mea, duo an mutat blandit deterruisset. Assum deterruisset an vix.

Ius omnium argumentum ea, has an nibh eius, ei mel dicta choro singulis. Mel no iriure sententiae, dolorem menandri patrioque in eum, saepe singulis atomorum vim id. Vim te epicurei reformidans, eum at posidonium complectitur. Lucilius legendos sit ei. Duo ut denique epicurei vituperatoribus.
